Avoiding tipping points in ecosystem based fisheries management: a non-parametric Bayesian approach

### 2014-05-13 manuscripts/manuscript.Rmd
latex symbols in tables now, using pandoc.table from pander

\appendix
\renewcommand\thefigure{\thesection.\arabic{figure}}

@@

Ricker Model
------------

@@

```{r, echo=FALSE, include=TRUE, fig.height=6, fig.cap="Traces from the MCMC estimates of the Ricker model show reasonable mixing (no trend) and sampling rejection rate (no piecewise jumps)", fig.width=6}
plot_ricker_traces
```

```{r, echo=FALSE, include=TRUE, fig.cap="Posteriors from the MCMC estimate of the Ricker model", fig.width=6, fig.height=4}
ggplot(ricker_posteriors, aes(value)) + 
  stat_density(geom="path", position="identity", alpha=0.7) +
  facet_wrap(~ variable, scale="free", ncol=2)
```

@@

```{r echo=FALSE, results = "asis", include = TRUE, cache=FALSE}
xtable::xtable(ricker_priors_xtable,
  caption = "Parameterization range for the uniform priors in the Ricker model", 
  sanitize.text.function = identity)
```

Myers Model
-----------

@@

```{r, echo=FALSE, include=TRUE, fig.height=6, fig.cap="Traces from the MCMC estimates of the Myers model show reasonable mixing (no trend) and sampling rejection rate (no piecewise jumps)", fig.width=6}
plot_myers_traces
```

```{r, echo=FALSE, include=TRUE, fig.cap="Posterior distributions from the MCMC estimates of the Myers model", fig.width=6, fig.height=6}
ggplot(myers_posteriors, aes(value)) + 
  stat_density(geom="path", position="identity", alpha=0.7) +
  facet_wrap(~ variable, scale="free", ncol=2)
```

@@

```{r echo=FALSE, results="asis", include = TRUE, cache=FALSE}
xtable::xtable(myers_priors_xtable,
           caption = "Parameterization range for the uniform priors in the Myers model",
           sanitize.text.function = identity)
```

Allen model
-----------

@@

```{r, echo=FALSE, include=TRUE, fig.height=6, fig.cap="Traces from the MCMC estimates of the Allen model show reasonable mixing (no trend) and sampling rejection rate (no piecewise jumps)", fig.width=6}
plot_allen_traces
```

```{r, echo=FALSE, include=TRUE, fig.cap="Posteriors from the MCMC estimate of the Allen model", fig.width=6, fig.height=6}
ggplot(allen_posteriors, aes(value)) + 
  stat_density(geom="path", position="identity", alpha=0.7) +
  facet_wrap(~ variable, scale="free", ncol=2)
```

@@

```{r echo=FALSE, results = "asis", include=TRUE, cache=FALSE}
xtable::xtable(allen_priors_xtable,
  caption = "Parameterization range for the uniform priors in the Allen model",
  sanitize.text.function = identity)
```

@@

```{r echo=FALSE, include=TRUE, fig.cap = "Traces from the MCMC estimates of the GP model show reasonable mixing (no trend) and sampling rejection rate (no piecewise jumps)"}
gp_assessment_plots$traces_plot
```

```{r echo=FALSE, include=TRUE, fig.cap="Posterior distributions from the MCMC estimate of the GP model. Prior curves shown in red."}
gp_assessment_plots$posteriors_plot
```

>>>>

\appendix
\renewcommand\thefigure{S.\arabic{figure}}

@@

@@

```{r, fig.height=6, fig.cap="Traces from the MCMC estimates of the Ricker model show reasonable mixing (no trend) and sampling rejection rate (no piecewise jumps)", fig.width=6}
plot_ricker_traces
```

```{r, fig.cap="Posteriors from the MCMC estimate of the Ricker model", fig.width=6, fig.height=4}
ggplot(ricker_posteriors, aes(value)) + 
  stat_density(geom="path", position="identity", alpha=0.7) +
  facet_wrap(~ variable, scale="free", ncol=2)
```

@@

```{r, results = "asis"}
pander::pandoc.table(ricker_priors_xtable,
  caption = "Parameterization range for the uniform priors in the Ricker model")
```

@@

```{r, fig.height=6, fig.cap="Traces from the MCMC estimates of the Myers model show reasonable mixing (no trend) and sampling rejection rate (no piecewise jumps)", fig.width=6}
plot_myers_traces
```

```{r, fig.cap="Posterior distributions from the MCMC estimates of the Myers model", fig.width=6, fig.height=6}
ggplot(myers_posteriors, aes(value)) + 
  stat_density(geom="path", position="identity", alpha=0.7) +
  facet_wrap(~ variable, scale="free", ncol=2)
```

@@

```{r, results="asis"}
pander::pandoc.table(myers_priors_xtable,
           caption = "Parameterization range for the uniform priors in the Myers model")
```

@@

```{r, fig.height=6, fig.cap="Traces from the MCMC estimates of the Allen model show reasonable mixing (no trend) and sampling rejection rate (no piecewise jumps)", fig.width=6}
plot_allen_traces
```

```{r, fig.cap="Posteriors from the MCMC estimate of the Allen model", fig.width=6, fig.height=6}
ggplot(allen_posteriors, aes(value)) + 
  stat_density(geom="path", position="identity", alpha=0.7) +
  facet_wrap(~ variable, scale="free", ncol=2)
```

@@

```{r, results = "asis"}
pander::pandoc.table(allen_priors_xtable,
  caption = "Parameterization range for the uniform priors in the Allen model")
```

@@

```{r, fig.cap = "Traces from the MCMC estimates of the GP model show reasonable mixing (no trend) and sampling rejection rate (no piecewise jumps)"}
gp_assessment_plots$traces_plot
```

```{r, fig.cap="Posterior distributions from the MCMC estimate of the GP model. Prior curves shown in red."}
gp_assessment_plots$posteriors_plot
```
